Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-08 method.tex
fir
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@984 ccdd05d5-56c1-461a-bf98-85f6876523b4

Equation~(\ref{eq:SNRTD}) can be implemented in the time-domain as an
\fir\ filter, requiring $\mathcal O(\numtmps \tmpsamps)$ floating point
operations per sample.  However, it is typically much more computationally
efficient to use the convolution theorem and the \fft\ to implement fast
convolution in the frequency-domain, requiring only $\mathcal O(\numtmps
\lg \tmpsamps)$ operations per sample with increased latency.

>>>>

Equation~(\ref{eq:SNRTD}) can be implemented in the time-domain as an
finite impulse response (\fir) filter, requiring $\mathcal O(\numtmps
\tmpsamps)$ floating point operations per sample.  However, it is typically
much more computationally efficient to use the convolution theorem and the
\fft\ to implement fast convolution in the frequency-domain, requiring only
$\mathcal O(\numtmps \lg \tmpsamps)$ operations per sample with increased
latency.
